Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-11-30 paper-kelompok/main.tex
accuracy-glucose

\author{\IEEEauthorblockN{Alzana Armaniar Farhani}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
farhanialzana@gmail.com}
\and
\IEEEauthorblockN{Balkan Khilmi Assakandari}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
balkankhilmi@gmail.com}
\and
\IEEEauthorblockN{Anindhita Nayazirly}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
zirlysukarno@gmail.com}
\newlineauthors
\IEEEauthorblockN{Akhmadi Surawijaya}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
email}
\and
\IEEEauthorblockN{Muhammad Ogin Hasanuddin}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
email}
}

@@

% Pendahuluan
\section{Results and Discussion}
\subsection{Accuracy}
\subsection{Repeatability}
\subsection{Wavelength Range}
\subsection{Device and DMF Cartridge Distance}
\subsection{Electronic Display Size}
\subsection{Weight and Size}

>>>>

\author{\IEEEauthorblockN{
    Alzana Armaniar Farhani\IEEEauthorrefmark{1},
    Balkan Khilmi Assakandari\IEEEauthorrefmark{2},
    Anindhita Nayazirly\IEEEauthorrefmark{3}, \\
    Akhmadi Surawijaya\IEEEauthorrefmark{4},
    Muhammad Ogin Hasanuddin\IEEEauthorrefmark{5}}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
\IEEEauthorrefmark{1}farhanialzana@gmail.com,
\IEEEauthorrefmark{2}balkankhilmi@gmail.com,
\IEEEauthorrefmark{3}zirlysukarno@gmail.com,
email,
email
}
}

@@

\section{Results and Discussion}
\subsection{Accuracy}
A glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich) was used to colorize glucose sample of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
The resulting liquid was then dropped between two microscope slides spaced 1 mm apart as shown in Fig. \ref{mic_slide}.

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.8]{mic_slide.png}}
    \caption{Glucose measurement setup}
    \label{mic_slide}
    \end{figure}

Fig.~\ref{glucose_result} shows the measurement results of the glucose experiment with manual baseline correction using linear regression.
Peak absorbance were measured 0.155 at 519 nm for 40 {\textmu}g/ml and 0.079 at 526 nm for 60 {\textmu}g/ml.
Absorbance for the 40 {\textmu}g/ml sample turned out higher than the 60 {\textmu}g/ml sample.
This result does not fit the absorbance-concentration relation of the Beer-Lambert law.
It was also observed that the 40 {\textmu}g/ml sample appeared darker for the naked eye.
Thus, a retest of the chemical reactions were due.

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{glucose-res.png}}
    \caption{Glucose absorbance spectrum measurement result, baseline corrected}
    \label{glucose_result}
    \end{figure}

Aside from glucose, we have tested the spectrophotometer with food dye measurements.
Blue, red, and yellow food dyes were mixed with water.
The volume percentage used were 0.033\%, 0.040\%, 0.050\%, 0.067\%, and 0.100\%.
The mixture was then dropped to the DMF cartridge as shown in Fig. \ref{dye_setup}.
The cartridge consisted of a DMF cartridge PCB, a layer of stretched parafilm, and a layer of silicon oil underneath the droplet;
a layer of silicon oil, a layer of stretched parafilm, and a layer of ITO above the droplet.

\begin{figure}[htbp]
    \centerline{\includegraphics[angle=90,scale=0.12]{dye-cartridge.jpg}}
    \caption{Food dye measurement setup}
    \label{dye_setup}
    \end{figure}

\subsection{Repeatability}
\subsection{Wavelength Range}
\subsection{Device and DMF Cartridge Distance}
\subsection{Electronic Display Size}
\subsection{Weight and Size}
